### 2019-02-20 sections/relatedwork.tex
added more about BPEL

\BPEL~\cite{bpel} is another popular business process language. The standardised
language allows for the specification of actions within business processes,
using an \XML format. Processes specified in \BPEL are executable, just like \YAWL.

\fixme{Is this higher order? What combinators can be used? Other limitations?}

>>>>

\BPEL~\cite{bpel} is another popular business process language. The standardised
language allows for the specification of actions within business processes,
using an \XML format.
The language is mainly used for coordinating web services.
Two workflow patterns are supported; execution of services can be done sequential or in parallel.
On top of that, processes can be guarded by conditionals.
There is no support for higher order processes however.
Processes described in \BPEL can be regarded as activity graphs, and they can also be rendered as such.
The specified processes in \BPEL are directly executable, just like \YAWL.
